Query Optimization for Dynamic Imputation

### 2017-03-01 paper/relatedwork.tex
paper: one more relevant reference
paper: minor changes in related work

@@

Imputation of missing values is a widely studied field within the statistics and machine
learning communities. As highlighted in~\cite{gelman2006data}, missing data
can appear for a variety of reasons, including both random and conditioned on
existing values (observed and missing). Methods in the statistical community
focus on correctly modeling relationships between the attributes to factor in
varied forms of missingness. For example, Burgette and Reiter~\cite{burgette2010multiple} discuss the usage of sequential regression trees
for imputing missing data.

@@

\subsection{Missing Values and Databases}
There is a long history in the database community surrounding the
treatment of \nullv{}. As early as 1973,~\cite{codd1973understanding}
provided a treatment of the semantics of \nullv{}. Multiple
papers have described various (at times conflicting) treatments
of nulls~\cite{grant1977null}. \ProjectName's main design invariant - no relational operator
sees missing values for attributes it must operate on and users should never see
missing data - eliminates
the need to handle \nullv{} value semantics, while guaranteeing query evaluation soundness.

@@

>>>>

There is related work in three primary areas: statistics, database research, and forecasting.

@@

Imputation of missing values is widely studied in the statistics and machine
learning communities. As highlighted in~\cite{gelman2006data}, missing data
can appear for a variety of reasons.
It can be missing uniformly at random and or conditioned on
existing values (observed and missing). Methods in the statistical community
focus on correctly modeling relationships between attributes to account for different forms of missingness. For example, Burgette and Reiter~\cite{burgette2010multiple} discuss the usage of sequential regression trees
for imputing missing data.

@@

\subsection{Missing Values and Databases}
There is a long history in the database community surrounding the
treatment of \nullv{}. As early as 1973,~\cite{codd1973understanding}
provided a treatment of the semantics of \nullv{}. Multiple
papers have described various (at times conflicting) treatments
of nulls~\cite{grant1977null}. \ProjectName's main design invariant---no relational operator
sees missing values for attributes it must operate on and users should never see
missing data---eliminates
the need to handle \nullv{} value semantics, while guaranteeing query evaluation soundness.

@@

\cite{fischer2013towards} describe the architecture of a DBMS with integrated forecasting operations for time-series, detailing
the abstractions necessary to do so.
